### 2020-11-14 thesis/chap_1.tex
continuating

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/hist_chap1.png}
}
 \caption[Histograms of flow values for all species and scenarios, comparing timesteps 2010 (observed) with 2100 (predicted)]{
 Histograms of flow values (results of Circuitscape runs for study region) for the years 2010 and 2100. This compares the observed values for the year 2010 (in blue, i.e. connectivity analysis of the land use map) with the current values of the model output in 2100 (in red, connectivity analysis of the year 2100 of the output of the land use change model). Note that the results are facetted by species and by scenario combination.}
 \label{fig:hist_1}
\end{figure}

>>>>

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/hist_chap1.png}
}
 \caption[Histograms of flow values for all species and scenarios, comparing timesteps 2010 (observed) with 2100 (predicted)]{Histograms of flow values (results of Circuitscape runs for study region) for the years 2010 and 2100. This compares the observed values for the year 2010 (in blue, i.e. connectivity analysis of the land use map) with the current values of the model output in 2100 (in red, connectivity analysis of the year 2100 of the output of the land use change model). Note that the results are facetted by species and by scenario combination.}
 \label{fig:hist_1}
\end{figure}

### 2020-11-14 thesis/chap_2.tex
continuating

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Regional_AC.png}
}
\caption{Cartography of opportunity and challenges  with the highest importance and diversity metric (for sub-regional tables) - summary from workshop results.}
\label{fig:reg_AC}
\end{figure}
\clearpage

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Transversal_AC.png}
}
\caption{Cartography of opportunity and challenges  with the highest importance and diversity metric (for regional tables) - summary from workshop results.}
\label{fig:trans_AC}
\end{figure}
\clearpage

@@

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Regional.png}
}
\caption{Cartography of priority areas and links (for sub-regional tables) - summary from workshop results.}
\label{fig:reg}
\end{figure}
\clearpage

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Transversal.png}
}
\caption{Cartography of priority areas and links (for regional tables) - summary from workshop results.}
\label{fig:trans}
\end{figure}
\clearpage

@@

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/bar_chap2.png}
}
\caption{Land use class frequencies in 2010 (observed) and 2100 (predicted) for the BAU and conservation scenarios (under baseline climate scenario).}
\label{fig:bar_chap2}
\end{figure}

@@

% Linear
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/connectivity_decrease_x5species_chap2.png}
}
 \caption{Change in mean flow (in \% of the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with other conservation scenarios - linear graph.}
 \label{fig:flow_linear_2}
\end{figure}

% Radar
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/radar_ggradar_chap2.png}
}
 \caption{Change in mean flow (in \% of the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with other conservation scenarios - radar graph.}
 \label{fig:flow_radar_2}
\end{figure}

% Histograms
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/hist_chap2.png}
}
 \caption{Histograms of flow values for all species and scenarios, for 2010 (observed) and 2100 (predicted).}
 \label{fig:hist_2}
\end{figure}

@@

% Linear
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_chap2.png}
}
 \caption{Change in the number of features (in \% of the 2010 flow) identified by the SURF analysis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - linear graph.}
 \label{fig:surf_linear_2}
\end{figure}

% Radar
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_radar_chap2.png}
}
 \caption{Change in the number of features (in \% of the 2010 flow) identified by the SURF analysis between 2010 (observed) and 2100 (predicted), contrasting BAU scenario with other conservation scenarios - radar graph.}
 \label{fig:surf_radar_2}
\end{figure}

>>>>

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Regional_AC.png}
}
\caption[Map of "opportunity" and "challenges", subregional tables - summary from workshop results (French)]{Map of "opportunity" and "challenges" resulting from the consensual mapping exercices. During our workshop, the study region was divided in multiple subregions, for each a singular table was set up. For each table, the two elements identified by workshop participants as "oportunity" and "challenges", and which scored the highest in both importance and agreement are identified on the map.}
\label{fig:reg_AC}
\end{figure}
\clearpage

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Transversal_AC.png}
}
\caption[Map of "opportunity" and "challenges", regional tables - summary from workshop results (French)]{Map of "opportunity" and "challenges" resulting from the consensual mapping exercices. During our workshop, the study region was divided in multiple subregions, and two tables were set up for the entire region. For these tables, the elements identified by workshop participants as "oportunity" and "challenges", and which scored the highest in both importance and agreement are identified on the map.}
\label{fig:trans_AC}
\end{figure}
\clearpage

@@

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Regional.png}
}
\caption[Map of priority areas and links, subregional tables - summary from workshop results (French)]{Map of priority areas and links esulting from the consensual mapping exercices.During our workshop, the study region was divided in multiple subregions, for each a singular table was set up. For each tables, different sets of priority areas (Red) and links (green) were identified and mapped.
}
\label{fig:reg}
\end{figure}
\clearpage

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.3\textwidth]{thesis/figures/Transversal.png}
}
\caption[Map of priority areas and links, regional tables - summary from workshop results (French)]{Map of priority areas and links esulting from the consensual mapping exercices.During our workshop, the study region was divided in multiple subregions, and two tables were set up for the entire region. For these tables, different sets of priority areas (Red) and links (green) were identified and mapped.
}
\label{fig:trans}
\end{figure}
\clearpage

@@

\begin{figure}[h!]
\makebox[\textwidth]{
\includegraphics[width=1.2\textwidth]{thesis/figures/bar_chap2.png}
}
 \caption[Land use class fequencies in 2010 and 2100 for the BAU and Conservation scenarios]{Land use class fequencies (in hectares) for Forest, Agriculture and Urban, in 2010 (observed from the land use data) and 2100 (predicted by the land use change model) for the BAU (Business As Usual) and Conservation scenarios (Note: these predictions are done under baseline climate scenario). Ref = Reforestation, Corrs Protection = Corridors Protection.}
\label{fig:bar_chap2}
\end{figure}

@@

% Linear
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/connectivity_decrease_x5species_chap2.png}
}
  \caption[Linear graph of change in mean flow (decrease in \% of the baseline 2010 flow) between 2010 (observed) and 2100 (predicted), comparing BAU scenario with conservation scenarios]{Linear graph of change in mean flow (decrease in \% of the baseline 2010 flow) between 2010 (observed) and 2100 (predicted). This compares the BAU (Business As Usual) scenario with conservation scenarios, facetted by species. Note that the line type represents the different climate scenarios so as to represent all scenario combinations (R = Reforestation, R(T) = Reforestation Targeted, CorPr = Corridors Protected).}
 \label{fig:flow_linear_2}
\end{figure}

% Radar
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/radar_ggradar_chap2.png}
}
  \caption[Radar graph of change in mean flow (decrease in \% of the baseline 2010 flow) between 2010 (observed) and 2100 (predicted), comparing BAU scenario with conservation scenarios]{Radar graph of change in mean flow (decrease in \% of the baseline 2010 flow) between 2010 (observed) and 2100 (predicted). This compares the BAU (Business As Usual) scenario with conservation scenarios, for all 5 species. Note that the line color represent species and that each side of the graph is a different scenario combination (R = Reforestation, R(T) = Reforestation Targeted, CorPr = Corridors Protected).}
 \label{fig:flow_radar_2}
\end{figure}

% Histograms
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.25\textwidth]{thesis/figures/hist_chap2.png}
}
  \caption[Histograms of flow values for all species and scenarios, comparing timesteps 2010 (observed) with 2100 (predicted)]{Histograms of flow values for the years 2010 \& 2100. This compares the observed values for 2010 (in blue) with the values of the model output in 2100 (in red). Results are facetted by species and scenario combination.}
 \label{fig:hist_2}
\end{figure}

@@

% Linear
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_chap2.png}
}
   \caption[Linear graph of change in the number of features (decrease in \% of the baseline 2010 numbers) between 2010 (observed) and 2100 (predicted), comparing BAU scenario with conservation scenarios]{Linear graph of change in the number of features (decrease in \% of the baseline 2010 numbers) between 2010 (observed) and 2100 (predicted). This compares the BAU (Business As Usual) scenario with conservation scenarios, facetted by species. Note that the line type represents the different climate scenarios so as to represent all scenario combinations (R = Reforestation, R(T) = Reforestation Targeted, CorPr = Corridors Protected).}
 \label{fig:surf_linear_2}
\end{figure}

% Radar
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/surf_radar_chap2.png}
}
 \caption[Radar graph of change in number of features (decrease in \% of the baseline 2010 numbers) between 2010 (observed) and 2100 (predicted), comparing BAU scenario with conservation scenarios]{Radar graph of change in number of features (decrease in \% of the baseline 2010 numbers) between 2010 (observed) and 2100 (predicted). This compares the BAU (Business As Usual) scenario with conservation scenarios, for all 5 species. Note that the line color represent species and that each side of the graph is a different scenario combination (R = Reforestation, R(T) = Reforestation Targeted, CorPr = Corridors Protected).}
 \label{fig:surf_radar_2}
\end{figure}
